Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-27 pecomplexity.tex
add some supporting paragraphs

@@

>>>>

In figure~\ref{fig:lma_pred_vs_ent} we directly compare the performance of LMA
to the value of the weighted permutation entropy for all runs of each program
under consideration. Largely, the data supports our hypothesized relationship
between prediction and WPE, namely that they are proportional. {\tt SVD} regime
1 bucks this trend a bit, having a larger WPE than might be expected from how
well its predictions are. We believe that this simply due to a limitation of the
WPE, namely that in the absence of any large features, as all the other regimes
have, the WPE falls back to the standard PE which the noisy behavior drives
toward 1.0.

@@

Figure~\ref{fig:lma_vs_arima} demonstrates that the LMA prediction algorithm is
better suited to the dynamics exhibited in the computer traces considered here,
except for the 1$^\text{st}$ regime of the {\tt SVD} program. There ARIMA
performs slightly better.
